---
title: "BIMM 143 Lec 11"
author: "Metztli Cisneros"
date: "May 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB Statistics

Download CSV file from PDB database <http://www.rcsb.org/stats/summary>. Read this into R and determine fraction of X-Ray structures

```{r}
pdb.stats <- read.csv("Data Export Summary.csv")
```

## Q1: What proportion of PDB entries does X-ray crystallography account for? What proportion of
structures are protein?

Lets calculate something

```{r}
percent <- (pdb.stats$Total / sum(pdb.stats$Total)) * 100
names(percent) <- pdb.stats$Experimental.Method
percent
```

## Q2: Type HIV in the search box on the home page and determine how many HIV-1 protease
structures are in the current PDB? - 793 entries










## Working with bio3d

```{r}
library(bio3d)

example("plot.bio3d")
```



```{r}
pdb <- read.pdb(file = "1hsg")

print(pdb)

attributes(pdb)
```

## To access individual attributes use $attribute
```{r}
head(pdb$atom)
```


Q8. Use the Bio3D write.pdb() function to write out a new C-alpha atom only PDB file for
viewing in VMD. 
```{r}
inds <- atom.select(pdb, "calpha")
inds
```

check if we have what we want
```{r}
head(pdb$atom[inds$atom,])
```

Looks good so lets continueto trim our PDB and write it out

```{r}
ca.pdb <-  trim.pdb(pdb, inds = inds)
ca.pdb
write.pdb(ca.pdb, file = "calpha_only.pdb")
```

```{r}
# Download some example PDB files
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
# Extract and align the chains we are interested in
pdbs <- pdbaln(files, fit = TRUE, exefile="C:/Users/ninem/Downloads/muscle.exe.exe")
# Print to screen a summary of the 'pdbs' object
pdbs
```


```{r}
aa <- get.seq("lake_A")
```

```{r}
b <- blast.pdb(aa)
```

